Using Poppr
========================================================

Here's an example of using Poppr.

```{r poppr1}
library(poppr)
```

Note that poppr version 1.1.0.99 is a development version.

Load an example dataset.

```{r poppr2}
data(Pinf)
Pinf
Pinf@pop.names
Pinf@ind.names
Pinf@other
```


The isolates from Mexico have been reported to be sexually recombining, while those from S. America are supposedly clonal.  Let's explore this.

First, let's separate the data into populations.

```{r poppr3}
Pinf.l <- seppop(Pinf)
```



```{r poppr4}
pop.l <- vector("list", length=4)
pop.l[[1]] <- mlg.table(Pinf.l[[1]], bar=T)
pop.l[[2]] <- mlg.table(Pinf.l[[2]], bar=T)
```


We can test for clonality using the index of association.

```{r poppr5}
pop.l[[3]] <- ia(Pinf.l[[1]], sample=999, quiet=T, valuereturn=T)
pop.l[[4]] <- ia(Pinf.l[[2]], sample=999, quiet=T, valuereturn=T)
```


Now let's clone correct.


```{r poppr6}
Pinf.l[[3]] <- clonecorrect(Pinf.l[[1]])
Pinf.l[[4]] <- clonecorrect(Pinf.l[[2]])
```


And see how this affects the number of MLGs in our dataset.

```{r poppr7}
pop.l[[5]] <- mlg.table(Pinf.l[[3]], bar=T)
pop.l[[6]] <- mlg.table(Pinf.l[[4]], bar=T)
```


And test the clone corrected dataset using the index of association.


```{r poppr8}
pop.l[[7]] <- ia(Pinf.l[[3]], sample=999, quiet=T, valuereturn=T)
pop.l[[8]] <- ia(Pinf.l[[4]], sample=999, quiet=T, valuereturn=T)
```


Now we can calculate a distance matrix for the data.


```{r poppr9}
Pinf.l[[5]] <- diss.dist(Pinf.l[[1]], frac=F)
Pinf.l[[6]] <- diss.dist(Pinf.l[[2]], frac=F)
Pinf.l[[7]] <- diss.dist(Pinf.l[[3]], frac=F)
Pinf.l[[8]] <- diss.dist(Pinf.l[[4]], frac=F)
```


We can make a minimum spanning network.

```{r poppr10}
Pinf.l[[9]] <- poppr.msn(Pinf.l[[1]], Pinf.l[[5]])
Pinf.l[[10]] <- poppr.msn(Pinf.l[[2]], Pinf.l[[6]])
```


Or neighbor-joining trees.

```{r poppr11}
library(ape)
Pinf.l[[11]] <- nj(Pinf.l[[5]])
Pinf.l[[12]] <- nj(Pinf.l[[6]])
plot(Pinf.l[[11]])
axis(side=1)
plot(Pinf.l[[12]])
axis(side=1)
```


And we can use k-means clustering to determine the number of groups.


```{r poppr12}
Pinf.l[[13]] <- find.clusters(Pinf.l[[1]], max.n = 20, n.pca = 10, scale = FALSE, choose.n.clust=F, quiet=T)
Pinf.l[[14]] <- find.clusters(Pinf.l[[2]], max.n = 20, n.pca = 10, scale = FALSE, choose.n.clust=F)
Pinf.l[[15]] <- find.clusters(Pinf.l[[3]], max.n = 20, n.pca = 10, scale = FALSE, choose.n.clust=F)
Pinf.l[[16]] <- find.clusters(Pinf.l[[4]], max.n = 20, n.pca = 10, scale = FALSE, choose.n.clust=F)

plot(1:20, Pinf.l[[13]]$Kstat, type='b', col=4, main="S. America")
plot(1:20, Pinf.l[[15]]$Kstat, type='b', col=4, main="S. America - CC")

plot(1:20, Pinf.l[[14]]$Kstat, type='b', col=4, main="N. America")
plot(1:20, Pinf.l[[16]]$Kstat, type='b', col=4, main="N. America- CC")
```

